---
title: "hw06_yukirang"
output: html_document
---
```{r}
library(gapminder)
library(tidyverse)
library(stringr)
library(ggplot2)
```

# 1. Character data
### String length
Try with different type of data, both the number and logical variable are trasferred to string.
```{r}
str_length(c("This", "is", 233, TRUE))
```
### Combining strings
```{r}
str_c("1", "22", "333")
```
Combining with a separater:
```{r}
str_c("Try", "this", sep = "%")
```
### Subsetting strings
str_sub() takes start and end arguments which give the (inclusive) position of the substring:
```{r}
(x <- c("We ", "ar e ", "family","!"))
str_sub(x, 2, 4)
```
### Locales
Changing case:
```{r}
str_to_upper(c("a", "i"))
```
Sorting by English alphabetically:
```{r}
str_sort(x, locale = "en")
```
Removing the wrapping spaces:
```{r}
str_wrap(x)
```
### Matching
1.Basic matching:
```{r}
str_view(x, "a")
```
Matching any character with "."
```{r}
str_view(x, ".a.")
```
2.Anchors
Start matching:
```{r}
str_view(x, "^a")
```
End matching:
```{r}
str_view(x, "y$")
```
3.Character classes and alternatives
```{r}
str_view(c("abc", "a.c", "a..c", "a.c."), "a[.]c")
```
Matching with a "|" character:
```{r}
str_view(c("brace", "bruce"), "br(a|u)c.")
```
### Repetition

```{r}
y <- "I'm loooooooving it!"
str_view(y, "oo?")
```
Specify a repitition time:
```{r}
str_view(y, "o{2,}")
```
### Tools
Detect matches:
```{r}
x
str_detect(x, "a")
```
Subsets:
```{r}
str_subset(words, "go$")
```
With filtering:
```{r}
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "go$")) %>% 
  knitr::kable()
```

Counting:
```{r}
z <- c("ah","haha","aaaaaa")
str_count(z, "a")
```
Mean:
```{r}
# The mean of  vowels per word
mean(str_count(z, "[aeiou]"))
```

Replacing matches:
```{r}
x <- c("Escape", "your", "comfort","zone")
# replace the first matching element
str_replace(x, "[aeiou]", "-")
# replace all matching element
str_replace_all(x, "[aeiou]", "-")
```
### Splitting

```{r}
(a <- sentences %>%
  head(6) %>% 
  #use "simplify = TRUE" to return a matrix
  str_split(" ", simplify = TRUE))
```
Find matches
```{r}
x
str_locate(x, "your")
```
### Other types of pattern
Apply regex() to control details of the match
Ignore the case:
```{r}
x
str_view(x, regex("e", ignore_case = TRUE))
```
coll(): compare strings using standard collation rules.
```{r}
a <- c("A", "a")
str_subset(a, coll("a", ignore_case = TRUE))
```
 use boundary() to match boundaries:
```{r}
x
str_extract_all(x, boundary("word"))
```
### Other uses of regular expressions
Searching from the global environment:
```{r}
apropos("split")
```

# 6. Work with a nested data frame
### Nest the data by country (and continent')
Let's first grab a sense of the data without nesting:
```{r}
gap_nested <- gapminder %>% 
   group_by(continent, country)
summary(gap_nested)
gap_nested %>% 
  head(10) %>% 
  knitr::kable()
```
And now nest the data:
```{r}
(gap_nested <- gap_nested %>% 
   nest())
```

We now see there are seperate tibbles for different countries.

### Fit a model of life expectancy against year
Let's see the change of lifeExp over year of China:
```{r}
(my_lm <- lm(lifeExp ~ log(gdpPercap), data=gap_nested[[25, "data"]]))
ggplot(gap_nested[[25, "data"]], aes(year, lifeExp)) +
    geom_point() +
    geom_smooth(method="lm") +
    ggtitle("Linear Regression Model Fitted of lifeExp against year on China")
  
```

### Apply a function map() and mutate()
```{r}
# the fitted model
my_lm <- function(df) {
  lm(lifeExp ~ I(year - 1950), data = df)
}
my_lm(gap_nested[[25, "data"]])
#map() the fitting function my_lm() to the 25th(China) and 26th(Colombia) elements of gap_nested$data.
fits <- map(gap_nested$data[25:26], my_lm)
fits
```
Scale this up to all countries:
```{r}
(gap_nested <- gap_nested %>% 
   mutate(fit = map(data, my_lm)))
```
Now we have an extra list of fitted linear models.

### Other information out of the linear models:
1."tidy" Intercept and  slope:
```{r}
library(broom)
tidy(gap_nested$fit[[25]]) %>% 
  knitr::kable()
```
Extend to all other countries:
```{r}
(gap_nested <- gap_nested %>% 
  mutate(tidy = map(fit, tidy)))
```
Now we have a tidy column of several tibbles.

2. One row summary using glance():
```{r}
glance(gap_nested$fit[[25]])
```
Looks like we get a bunch of statistical data:)

3. Augment the original data with other columns:
```{r}
augment(gap_nested$fit[[25]])
```
Now we have several colums, with the fitted rows of lifeExp.
4. unnest the data in the dataframe:
```{r}
(gap_coefs <- gap_nested %>% 
   select(continent, country, tidy) %>% 
   unnest())
```
5. Adding the previous scope and intercept with recode():
```{r}
(gap_coefs <- gap_coefs %>%
   mutate(term = recode(term,
                        `(Intercept)` = "intercept",
                        `I(year - 1950)` = "slope")))
```
6. Reshaping the estimates of each continents and make a summary:
```{r}
(gap_ests <- gap_coefs %>% 
   select(continent:estimate) %>% 
   spread(key = term, value = estimate))
gap_ests %>% 
  select(intercept, slope) %>% 
  summary()
```
6. Making a plot of the whole distribution:
```{r}
ggplot(gap_coefs, aes(x = estimate)) +
  geom_density() + 
  # assing a density projection on the x-axis
  geom_rug() +
  # using scales to expand the plot throughly
  facet_wrap(~ term, scales = "free")
```

Inspiration for the modelling and downstream inspiration：
* From the plot of linear regression model fitted on China, it is easy to notice that the linear model doesn't fitted very well. There is a dramatical change of lifeExp between 1950s and 1970s. And the the slope becomes smallers.
* From the residual we notice that during the high range of lifeExp, say 70+, it doesn't performs that well cause it stays negative and keeps going down. While from 58 to 70+, it keeps going done.

* From the std.error we can also find that the data of Zimbabwe, Rwanda and Swaziland seems not that suitable for our model.
Let's see what's going on:
```{r}
other <- gapminder %>% 
  filter(country == "Zimbabwe" | country == "Rwanda" | country == "Swaziland") %>% 
  data.frame()
other %>% 
  ggplot(aes(year, lifeExp, colour=country)) +
  geom_smooth(se = FALSE,method = "lm") + # fit linear regression
  geom_point() +
  ggtitle("Linear Regression Model Fitted of lifeExp against year")
```
What if we try some different methods? Mabe for one distinct country loess performs better. However this can be overfitting when it is extended.

```{r}
other %>% 
  filter(country == "Zimbabwe") %>% 
  ggplot(aes(year, lifeExp, colour = "country")) +
  geom_smooth(method = "loess") + # fit linear regression
  geom_point() +
  ggtitle("Linear Regression Model Fitted of lifeExp against year on Zimbabwe")
```

